\documentclass{article}

\PassOptionsToPackage{numbers,compress}{natbib}
\usepackage{neurips_2025}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{enumitem}

\title{ToolShift: Canonical-Action Evaluation under Real API Evolution}

\author{Anonymous Authors}

\newcommand{\toolshift}{\textsc{ToolShift}}
\newcommand{\CAA}{\textsc{CAA}}
\newcommand{\POC}{\textsc{POC}}
\newcommand{\NOS}{\textsc{NOS}}

\begin{document}

\maketitle

\begin{abstract}
\input{sections/abstract}
\end{abstract}

\input{sections/01_intro}
\input{sections/02_related}
\input{sections/02_protocol}
\input{sections/03_benchmark}
\input{sections/04_methods}
\input{sections/05_results}
\input{sections/06_analysis}
\input{sections/07_discussion}

\paragraph{Broader impact.}
Our benchmark studies tool-use reliability under API evolution, a setting directly relevant to production assistants and developer tools. Better evaluation can reduce silent failures when APIs deprecate fields, change scopes, or split capabilities. The main risk is over-claiming beyond the observable evidence. We therefore explicitly limit our strongest claim to \emph{schema-visible} evolution and report impossible-shadow boundary failures when no visible cue is available.

\paragraph{Reproducibility statement.}
All reported metrics come from deterministic evaluation pipelines and artifact summaries already stored in this repository. The paper is backed by a six-layer validation chain: evaluator correctness, execution sanity, request replay, official-document smoke tests, API-surface smoke tests, and frozen blind review. The exact artifact pointers used by this draft are listed in Appendix~\ref{app:artifacts}.

\bibliographystyle{unsrtnat}
\bibliography{refs}

\appendix
\input{sections/appendix}

\end{document}
