Tool-use agents increasingly face APIs that rename fields, split permissions, deprecate routes, and alter response contracts. Existing benchmarks mostly assume static tools or blur together semantics-preserving changes and true capability shifts. We introduce \toolshift, a benchmark and evaluation protocol for \emph{canonical semantic actions under real API evolution}. \toolshift{} uses set-valued canonical actions, separates positive transformations from negative near-orbits, audits an unambiguous core, and validates claims with a six-layer evidence chain spanning execution sanity, request replay, official-document checks, API-surface checks, and frozen blind review. We curate a real-evolution dev panel with 36 cases and 72 views across nine vendor families, and a disjoint frozen blind panel with 24 cases and 48 views across six family tags and five vendors. The strongest retained system, a description- and contract-aware scaffold baseline, is perfect on the dev panel and remains strongest on blind review with $\CAA=0.917$, $\CAA^{+}=1.000$, $\NOS=0.727$, and $\POC=1.000$; public-model baselines and a retrieval+rerrank document baseline degrade on the same blind negative families. A final teacher-distilled canonical-bottleneck SCC check raises dev-panel \NOS{} only from $0.606$ to $0.636$ while leaving $\CAA^{+}$ and \POC{} at $0.000$, so it does not support a learned-method claim. Protocol-reliability analysis shows that 10 of 11 blind negatives are dual-control admissible: collapsing them to a single-action protocol would trivially inflate blind \NOS{} to $1.000$ for all compared methods. Family bootstrap and leave-one-family-out analysis show that blind pressure is family-sensitive but not a one-family artifact. Mechanism analyses further show that current gains rely on localized description and contract cues and do not extend to hidden backend shifts. Taken together, \toolshift{} identifies schema-visible capability-gap inhibition as a distinct, measurable challenge in tool use and supports a benchmark-and-diagnosis contribution rather than a learned-method win.
